---
title: "Assignment2"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message    = FALSE,   # oculta mensajes
  warning    = FALSE,   # oculta warnings
  fig.align  = "center",
  fig.width  = 4.5,       # tama침o base de los gr치ficos (en pulgadas)
  fig.height = 3,
  dpi        = 120,
  out.width  = "70%",   # reduce tama침o en la p치gina
  fig.show   = "hold"   # agrupa varias figuras del chunk en el mismo bloque
)
```

```{r, include=FALSE}
# Clear plots
if(!is.null(dev.list())) dev.off()

# Clean workspace
rm(list=ls())
```

# 1. Data preparation
After checking the dataset, we observe that many variable's observation's are left in blank, we set it to NA because it's missing data.

```{r}
# Loading data
df <- read.csv("aug_train.csv", header=T)
summary(df)

df[df == ""] <- NA
# df$city = factor(df$city)
# df$gender = factor(df$gender)
# df$relevent_experience = factor(df$relevent_experience)
# df$enrolled_university = factor(df$enrolled_university)
# df$education_level = factor(df$education_level)
# df$major_discipline = factor(df$major_discipline)
# df$experience = factor(df$experience)
# df$company_size = factor(df$company_size)
# df$company_type = factor(df$company_type)
# df$last_new_job = factor(df$last_new_job)
```

## Removing duplicate or irrelevant observations
We find that there's no duplicates in terms of ID in the dataset.
```{r}
```

## Variables (NO HE SEPARAT PER NUM AND CAT PQ POTSER ALGUNA chr ES NUMERICA, 1. INSPECCIONAR VARIABLE I DESPRES DECIDIM )
We need to check the variables one by one in order to handle its missing data, filter unwanted outliers and regrouping for factors.

### enrollee_id
We confirm that `enrollee_id` does not have duplicates or missing data, as we wanted, because it's the variable that identifies each enrollee. 

But this variable is not necessary for modelling because it doesn't have predictive power, so we remove it.

```{r}
sum(duplicated(df$enrollee_id))
sum(is.na(df$enrollee_id))
```

### city
The variable `city` has 123 levels and no missing data, some cities show really low frequence.
This is a categorical variable, we convert it to factor.
```{r}
sum(is.na(df$city))
length(unique(df$city)) #check number of unique categories -> 123
table_city <- sort(table(df$city))
head(table_city)   # cities with less frequence

df$city <- factor(df$city)
```
### city_development_index
The variable `city_development_index` has no missing data and no outliers.
```{r}
sum(is.na(df$city_development_index))

summary(df$city_development_index)
hist(df$city_development_index)

# Outliers
boxplot(df$city_development_index, horizontal = T)
varout <- summary(df$city_development_index)
iqr = varout[5]-varout[2]
usout <- varout[5]+3*iqr
lsout <- varout[2]-3*iqr
umout <- varout[5]+3*iqr
lmout <- varout[2]-3*iqr

sev_out <- which((df$city_development_index > usout) | (df$city_development_index < lsout))
mild_out <- which((df$city_development_index > umout) | (df$city_development_index < lmout))

boxplot(df$city_development_index, horizontal = T)
abline(v=usout,col='orange', add = T)
abline(v=lsout,col='orange', add = T)
abline(v=umout,col='orange', add = T)
abline(v=lmout,col='orange', add = T)
sev_out #0
mild_out #0

# Distribution
hist(df$city_development_index, freq = F)
m = mean(df$city_development_index)
std = sd(df$city_development_index)
curve(dnorm(x,m,std),add=T, col="red")
```
### gender
The variable `gender` has 4508 NA and 4 unique categories: NA, Female, Male and Other.

To handle missing data, we'll create another category called Unknown, because removing 4508 rows means losing 23% of the dataset, and imputing Male/Female artificially introduces bias.

```{r}
sum(is.na(df$gender))
length(unique(df$gender)) #check number of unique categories
table_gender <- table(df$gender)

df$gender <- ifelse(is.na(df$gender), "Unknown", df$gender)
table_gender

df$gender <- factor(df$gender)
```
### relevent_experience
The variable `relevent_experience` does not have missing data and it has 2 levels: 'Has relevant experience' and 'No relevant experience'

```{r}
sum(is.na(df$relevent_experience))
length(unique(df$relevent_experience)) #check number of unique categories
table_relevent_experience<- table(df$relevent_experience)
table_relevent_experience

df$relevent_experience <- factor(df$relevent_experience)
```
### enrolled_university
The variable `enrolled_university` has 386 NA and 4 levels: NA, 'Full time course' and 'no_enrollment' and 'Part time course'.

Like the variable `gender`, we convert the NAs to category Unknown.

```{r}
sum(is.na(df$enrolled_university))
length(unique(df$enrolled_university)) #check number of unique categories
table_enrolled_university <- table(df$enrolled_university)
table_enrolled_university

df$enrolled_university <- ifelse(is.na(df$enrolled_university), "Unknown", df$enrolled_university)
table_enrolled_university

df$enrolled_university <- factor(df$enrolled_university)
```
### education_level
The variable `education_level` has 460 NA and 6 levels: NA, 'Graduate', 'High School','Masters','Phd' and 'Primary School'

We convert the NAs to category Unknown.

```{r}
sum(is.na(df$education_level))
length(unique(df$education_level)) #check number of unique categories
table_education_level <- table(df$education_level)
table_education_level

df$education_level <- ifelse(is.na(df$education_level), "Unknown", df$education_level)
table_education_level

df$education_level <- factor(df$education_level)
```
### major_discipline
The variable `major_discipline` has 2813 NA and 7 levels: NA, 'Arts', 'Business Degree','Humanities','No major','STEM' and 'Other'.

We convert the NAs to category Unknown???

```{r}
sum(is.na(df$major_discipline))
length(unique(df$major_discipline)) #check number of unique categories
table_major_discipline <- table(df$major_discipline)
table_major_discipline

df$major_discipline <- ifelse(is.na(df$major_discipline), "Unknown", df$major_discipline)
table_major_discipline

df$major_discipline <- factor(df$major_discipline)
```
### experience
The variable `experience` has 65 NA and 23 levels from <1 to >20. We should convert it to a numerical variable??????


```{r}
sum(is.na(df$experience))
length(unique(df$experience)) #check number of unique categories
table_experience <- table(df$experience)
barplot(table_experience)
```

# 2. Profiling and Feature Selection




# 3. Modeling using numeric variables using transformations if needed



# 4. Residual analysis: unusual and influent data filtering




# 5. Adding factor main effects to the best model containing numeric variables





# 6. Residual analysis: unusual and influent data filtering





# 7. Adding factor main effects and interactions (limit your statement to order 2) to the best model containing numeric variables




# 8. Final Residual analysis: unusual and influent data filtering. Iterative process could be needed




# 9. Goodness of fit and Model Interpretation
